Verifying Demonstrations

### 2021-06-17 paper/protocol-trusted.tex
Clarifies intro to trusted protocol

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
  Anyone can do this, but in general, there is only one organizer.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs of participation to protesters.
  The proofs are constructed such that they are verifiable by third parties.
  The witness must be trusted by the verifier.
\end{enumerate}
Anyone can be a verifier (we required universal verifiability, 
\cref{desired-properties}).
The verifier defines the protest to be counted by setting the cause, time 
(interval) and location (area), \cf \cref{DefProtest}.
Now the verifier counts all proofs that verify correctly and fulfils the cause, 
time and location criteria.
The verifier can publish, \eg in a news paper, the final count together with 
the cause, time and location and anyone can verify this count (by the same 
procedure).

>>>>

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
  Anyone can do this, but in general, there is only one organizer.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs of participation to protesters.
  The proofs are constructed such that they are verifiable by third parties.
  The witness must be trusted by the verifier.
\end{enumerate}
Anyone can be a verifier (we required universal verifiability, 
\cref{desired-properties}).
The verifier defines the protest to be counted by setting the cause, time 
(interval) and location (area), \cf \cref{DefProtest}.
Now the verifier counts all proofs that verify correctly and fulfils the cause, 
time and location criteria.
The verifier can publish, \eg in a news paper, the final count together with 
the cause, time and location and anyone can verify this count (by repeating the 
same procedure).
Any participant can confirm their inclusion by repeating the count and checking 
that their proof is included.
